---
title: "Homework-21.qmd"
format: html
editor: visual
---
Clear the decks
```{r}
rm(list = ls())
```
Libraries I always use
```{r}
library(dplyr)
library(ggplot2)
```
Import the data
```{r}
library(here)
lady <- read.csv(here("Data","ladybirds.csv"))
```
Check it out
```{r}
glimpse(lady)
```
Convert variables to factor
```{r}
lady <- lady %>% mutate(Habitat = as.factor(Habitat))
lady <- lady %>% mutate(Site = as.factor(Site))
lady <- lady %>% mutate(colour = as.factor(colour))
```
Summarize data
```{r}
totals <- lady %>%
  group_by(Habitat, colour) %>%
  summarise(total.number = sum(number))
```
Summarize raw data
```{r}
ggplot(totals, aes(x = Habitat, y = total.number, fill = colour)) + geom_bar(stat = 'identity', position = 'dodge')
```
Customize colors used to represent groups of data
```{r}
ggplot(totals, aes(x = Habitat, y = total.number, fill = colour)) + geom_bar(stat = 'identity', position = 'dodge') + scale_fill_manual(values = c(black = "black", red = "red"))
```
Give function a matrix of total counts
```{r}
totals
```
Cross(x)-tabulation
```{r}
lady.mat <- xtabs(number ~ Habitat + colour, data = lady)
lady.mat
```
Chi-squared test
```{r}
chisq.test(lady.mat)
```
Assign chi squared values to a name and look at mechanics of test
```{r}
lady.chi <- chisq.test(lady.mat)
names(lady.chi)
lady.chi$expected
```
Read in ozone data
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(here)
ozone <- read.csv(here("Data","ozone.csv"))
```
Examine ozone data
```{r}
glimpse(ozone)
```
Convert variables to factor
```{r}
ozone <- ozone %>% mutate(Garden.location = as.factor(Garden.location))
ozone <- ozone %>% mutate(Garden.ID = as.factor(Garden.ID))
```
Stack histograms on top of each other
```{r}
ggplot(ozone, aes(x = Ozone)) + geom_histogram(binwidth = 10) + facet_wrap(~ Garden.location, ncol = 1) + theme_bw()
```
Do a t-test
```{r}
t.test(Ozone ~ Garden.location, data = ozone)
```
Test for equality of variance in two-sample t-test
```{r}
var.test(Ozone ~ Garden.location, data = ozone)
```

