---
title: "Homework-16.qmd"
format: html
editor: visual
---
Clearing R's environment and turning on tidyverse and here packages.
```{r}
rm (list = ls())
library(tidyverse)
library(here)
```
Creating the new data frame "cover" with the donnerville_percent_cover.csv data. Although I understand it would have been ideal for R to read from the data folder in here, /Users/AddieMoore/Library/CloudStorage/OneDrive-St.LawrenceUniversity/Biostats/Moore-Biostats-HW, the file did not appear in Rstudio because OneDrive is still unsyncing every time so I imported it a different way. 
```{r}
library(readr)
cover <- read_csv("~/Desktop/donnerville_percent_cover.csv")
```
Examining the data using view to view the data set in a new tab and str to look at the structure of the data.
```{r}
view(cover)
str(cover)
```
Changing column names
```{r}
colnames(cover) <- c("site", "date", "plot_type", "plot_dim", "slope", "aspect", "plot", "cover_type", "percent")
```
Changing site, plot_type, and cover_type column variables from character data to factor data.
```{r}
cover$site <- as.factor(cover$site)
cover$plot_type <- as.factor(cover$plot_type)
cover$cover_type <- as.factor(cover$cover_type)
```
Changing date column variables from character data to date data. 
```{r}
cover$date <- dmy(cover$date)
```
Finding average percent cover for bare, bryophytes, and vascular plants in Donnerville 1.
```{r}
bare <- data.frame(n = c(95.0, 95.0, 70.0, 50.0))
mean (bare$n)
bryophytes <- data.frame(n= c(0, 0, 10))
mean (bryophytes$n)
vascular <- data.frame(n = c(5.0, 30.0, 40.0))
mean(vascular$n)
```

```{r}
mean(cover$percent[cover$cover_type == "Vascular"])
```
