---
title: "Homework 24"
format: html
editor: visual
---

## Overview

For your homework you will implement a data analysis using a dataset on crab growth measurements.

Set things up (hint: there is a new package to add with `library()`)

```{r}
rm (list = ls())
library(tidyverse)
library(ggfortify)
library(here)
```

## The data

Let's pull in some data appropriate biologists: crab measurements. This dataset includes measurements of farmed crabs.

```{r}
crabs <- read.csv(here("Data", "CrabAgePrediction.csv"))
glimpse(crabs)
```

One of the variables is categorical - let's fix that in the data.

```{r}
crabs$Sex = as.factor(crabs$Sex)
```

## Question

Is there a relationship between height and weight in female crabs?

1.  Extract the data for just female crabs.
```{r}
female_crabs <- filter(crabs, Sex == "F")
```

2.  Examine the response and predictor variables and use the flow chart from class to decide the appropriate statistical analysis (choose from: chi-square, 2-sample t-test or linear regression). Explain your answer here:
```{r}
# We are just looking for a relationship between height and weight, and there is not one variable that is established as being a predictor and one as a response, so the analysis could be run with either height or weight functioning as predictor/response. Both height and weight are ratio data which is a continuous predictor variable, so the test has to be a linear regression. It can not be a chi-squared test because that would require a discrete predictor variable or a 2-sample t-test because that would require a categorical predictor variable.  
```

3.  Work through the data analysis **following all of the steps provided in chapter 5 of your book**. You may use class notes or homework keys as a guide.

```{r}
# Linear regression
model_fc <- lm(Weight ~ Height, data = female_crabs)

# Assumptions
autoplot(model_fc, smooth.colour = NA)

# Interpretation
anova(model_fc)
summary(model_fc)

# Plotting data with linear regression line
ggplot(female_crabs, aes(x = Height, y = Weight)) + geom_point() + geom_smooth(method = 'lm')

# There appears to be a relationship between height and weight in female crabs (p < 0.001)
```

## 
