---
title: "Homework-18.qmd"
format: html
editor: visual
---

Setting up.

```{r}
rm (list = ls())
library(tidyverse)
library(here)
```

Reading in dataset from desktop since OneDrive is disconnected. There is a copy of the csv in the Data folder but it is greyed out.

```{r}
library(readr)
compensation <- read_csv("~/Desktop/compensation.csv")
View(compensation)
```

Making a scatterplot.

```{r}
ggplot(compensation, aes(x = Root, y = Fruit)) + geom_point()
```

Getting rid of grey background in scatterplot.

```{r}
ggplot(compensation, aes(x = Root, y = Fruit)) + geom_point() + theme_bw()
```

Changing point size.

```{r}
ggplot(compensation, aes(x = Root, y = Fruit)) + theme_bw() + geom_point(size = 5)
```

Changing axis labels.

```{r}
ggplot(compensation, aes(x = Root, y = Fruit)) + theme_bw() + geom_point(size = 5) + xlab("Root Biomass") + ylab("Fruit Production")
```

Changing colors to show specific groups.

```{r}
ggplot(compensation, aes(x = Root, y = Fruit, color = Grazing)) + theme_bw() + geom_point(size = 5) + xlab("Root Biomass") + ylab("Fruit Production")
```

Making a box and whisker plot.

```{r}
ggplot(compensation, aes(x = Grazing, y = Fruit)) + geom_boxplot() + geom_point(size = 4, color = 'lightgrey', alpha = 0.5) + xlab("Grazing treatment") + ylab("Fruit Production") + theme_bw()
```

Making a histogram that shows fruit production.

```{r}
ggplot(compensation, aes(x = Fruit)) + geom_histogram()
```

Defining bin number.

```{r}
ggplot(compensation, aes(x = Fruit)) + geom_histogram(bins = 15)
```

Produce graph matrix that is organized by data type (factor, categorical)

```{r}
ggplot(compensation, aes(x = Fruit)) + geom_histogram(bins = 15) + facet_wrap(~Grazing)
```

Saving graphs as a .png.

```{r}
ggsave("ThatCoolHistorgamofFruit.png")
```
